---
title: "Analysis LEZ 2"
author: '41783'
date: "25/02/2020"
output: 
  html_notebook:
    code_folding: show
    # keep_md: true
    df_print: paged
---

Basic configuration and loading of packages:

```{r setup, include=FALSE}
# rm(list = ls())
knitr::opts_chunk$set(
  echo = TRUE, 
  fig.align = "center",
  out.width = '80%'
)
```

```{r message=FALSE, warning=FALSE}
# library(jsonlite)
library(tidyverse)
library(rvest)

library(sf) # Geo analysis
# library("rgdal")

library(DBI) # SQL db

library(panelView)
library(lubridate)
```


## Index of contents

* Read data from pre-processing
  + Nuts regions geographies
  + data from capstone_db
    * nuts_time (outcomes, controls and mediators)
    * treatment from Umweltzonen
* Do explorative analysis on the volatility of outcomes
* Create variables of interest
* Do analysis




## Read data from pre-processing:

### Nuts Regions geographies 

```{r}
# Characteristics of nuts3:

nuts.sf <- readRDS("data/nuts_sf_final")

nuts.sf <- nuts.sf %>%
  dplyr::rename(
    geo = NUTS_ID,
    nuts_level = LEVL_CODE,
    country = CNTR_CODE,
    nuts_name = NUTS_NAME
  )

nuts.sf %>% as.data.frame() %>% head()
```

### Get data from SQLdb:

```{r}
db <- dbConnect(RSQLite::SQLite(), "data/capstonedb")
dbListTables(db)
```

Tables:

* airq_plans: List of (new) air quality plans
* nuts3: NUTS code, name and attainment status according to UAR and GZ, and minimum year for GZ
* umweltzonen: Treatment status of all zones in germany for each status with timing.
* nuts_time statistical data on NUTS regions (outcomes and controls)

#### Get nuts_time (outcomes, mediators and controls)

```{r}
dta <- dbGetQuery(db, "SELECT * from nuts_time")
dta %>% filter(time == 2006)
dta %>% names()
```

Create variables of interest (outcomes and controls)
(and possibly a restricted dataset only with those)

```{r}
## (for NUTS2)

### outcomes:

# hours worked per person (abseentism/temporality)
# (waiting to get data on hours)

dta <- dta %>%
  # dplyr::group_by(geo) %>% # 1000's hours/1000's employees
  mutate(hours_per_worker = hours_TOTAL/empl_TOTAL,
         hours_per_day = hours_per_worker/259) #approx

# Looks like correct
# dta %>%
#   ggplot() +
#   geom_histogram(aes(x = hours_per_day))

# wages per worker
# (waiting to get data on wages)

dta <- dta %>%
  # dplyr::group_by(geo) %>%
  mutate(wages_per_worker = 
           (wages_TOTAL*1000000)/(empl_TOTAL*1000), 
         wage_per_day = wages_per_worker/259) #approx

# # Looks like correct
# dta %>%
#   ggplot() +
#   geom_density(aes(x = wage_per_day))
# # +  facet_wrap(facets = vars(time))

# wage/hour worked (productivity?)

dta <- dta %>%
  # dplyr::group_by(geo) %>%
  mutate(wage_per_hour = 
           (wages_TOTAL*1000000)/(hours_TOTAL*1000)) #approx

# # Looks like correct
# dta %>%
#   ggplot() +
#   geom_density(aes(x = wage_per_hour))
# # +  facet_wrap(facets = vars(time))

# Unemployment
# (done)

# Employment rate (with respect to active pop or "wotking age pop")

dta <- dta %>%
  # dplyr::group_by(geo) %>%
  mutate(empl_rate_active = # both in thousands
           (empl_TOTAL*1000)/(active_T_Y_GE15*1000),
         empl_rate_wpop = # both in thousands
           (empl_TOTAL*1000)/pop_15_64)

## Some doubts left...
# dta$empl_rate_active %>% hist(breaks = 30) # Why above 1?
# dta$empl_rate_wpop %>% hist(breaks = 30)

 ### Controls: 

# Investment/capita (nuts 2)
# Educational level/capita (nuts 2)
# Dependency ratio (NUTS 2)

# Share of Women in the labor market
dta <- dta %>%
  # dplyr::group_by(geo) %>%
  mutate(active_F_share = # both in thousands
           `active_F_Y15-64`/`active_M_Y15-64`)

dta$active_F_share %>% hist(breaks = 30)

## (for NUTS 3)

### Outcomes:

# Proportion of working age population

# Dependency rate

### Controls
# mean age
# mortality and birth rate

dta %>% names()
 # others to do GDP and Productivity: GDP/capita, Investment/capita, wage levels, 
```


### Small analysis of the volatility of data:

```{r}
get_volatility <- function(data = dta, 
                           CNTR_CODE = "DE", 
                           time_vector = 2000:2019,
                           variable = "gdp_eur_hab",
                           cluster_differences = "nuts1" # can be "country"
){
  temp <- data %>%
    arrange(geo, time) %>%
    dplyr::mutate(nuts1 = substr(geo, 3, 4),
           country = substr(geo, 1, 2)) %>%
    filter(
      country == CNTR_CODE,
      # !is.element(time, c(2008, 2009, 2010, 2011)),
    ) %>%
    dplyr::group_by(geo) %>%
    dplyr::mutate(perc_change_unit = (eval(parse(text=variable))-lag(eval(parse(text=variable))))/lag(eval(parse(text=variable)))*100) %>%
    ungroup() %>%
    dplyr::group_by("nuts1", time) %>%
    dplyr::mutate(mean_change_group = mean(perc_change_unit, na.rm = TRUE),
           perc_change_dev = perc_change_unit - mean_change_group) %>%
    ungroup() %>%
    select(geo, time, variable, mean_change_group, perc_change_unit, perc_change_dev)
  print(temp %>% summary)
  return(temp)
}
```


```{r}
temp2 <- get_volatility(data = temp, CNTR_CODE = "DE",
                       time_vector = 2000:2019,
                       variable = "unempR_T")
# temp2

# pop_total, empl_EMP_TOTAL, inv_TOTAL, wages_TOTAL, mean_pol, 
```


### Nuts Regions geographies and treatment status

All nuts 3 and nuts 2 regions that had multiple LEZ were excluded from this data, so will have NA when I merge it with "dta".

```{r}
nuts_treated <- readRDS("data/nuts_sf_treated")

nuts_treated <- nuts_treated %>%
  dplyr::rename(
    geo = NUTS_ID,
    nuts_level = LEVL_CODE,
    country = CNTR_CODE,
    nuts_name = NUTS_NAME
  ) 

nuts_treated %>% as.data.frame() %>% head()
```

## Unite variables and treatment status:

```{r}
temp <- nuts_treated %>% 
  as.data.frame() %>%
  select(-geometry) %>%
  right_join(dta, by = "geo")
```

# Synthetic control method:

* ! Note: 
* ! This is being done with fake treatment groups that are really controls because the area was not taken into account.
* !


```{r}
# install.packages("Synth")
library(Synth)
# data(basque)
# basque
# ?Synth::dataprep()
# Synth::dataprep(foo = nuts_try, 
#                 predictors = values, # This is wrong
#                 dependent = values,
#                 unit.variable = NUTS_ID,
#                 time.variable = time,
#                 treatment.identifier = "HR043",
#                 )
# nuts_try
```

http://yiqingxu.org/teaching/17802/synth.pdf
https://www.stata.com/meeting/uk17/slides/uk17_Cerulli.pdf
https://blogs.worldbank.org/impactevaluations/evaluating-regulatory-reforms-using-the-synthetic-control-method
https://jech.bmj.com/content/72/8/673


## Generalized Synthetic control method (experiment)

1. Try with NUTS 2 regions. 
  - Variable: Unemployment rate total, case: Berlin
2. Try with NUTS 3 regions. 
  - Variable: Employed population rate, case: Aachen

```{r}
library(gsynth)
library(lubridate)

# Prepare data for NUTS 2 synthetic control -> Treatment var to dummy +  restrict controls

# Would be good to do this before.
temp %>%
  # Transformate treatment var into a dummy variable
  group_by(geo) %>%
  mutate(
    is_inagurated = as_date(Stage_1, format = "%d.%m.%Y") %>% year(),
    is_announced = as_date(Announcment, format = "%d.%m.%Y") %>% year(),
  ) %>%
  ungroup() %>%
  mutate(
    is_inagurated = case_when(
      is.na(is_inagurated) ~ 0, # If its control, never inagurated
      time < is_inagurated ~ 0, # If its before the inaguration
      TRUE ~ 1 # if neither, then its after
    ),
    is_announced = case_when(
      is.na(is_announced) ~ 0, # If its control, never
      time < is_announced ~ 0, # If its before
      TRUE ~ 1 # if neither, then its after
    )
  ) %>%
  select(geo, time, LEZ,
         Stage_1, is_inagurated,
         Announcment, is_announced,
         )  %>%
  filter(!is.na(Stage_1))

```


```{r}
data(gsynth)

# ?gsynth
turnout
simdata

# out <- gsynth(Y ~ D + X1 + X2, data = simdata, 
#               index = c("id","time"), 
#               force = "two-way", CV = TRUE, 
#               r = c(0, 5), se = TRUE, 
#               inference = "parametric", nboots = 1000, 
#               parallel = FALSE)


```


```{r}
# install.packages('gsynth', type = 'source')
library(gsynth)

out2 <- gsynth(gdp_eur_hab ~ treat_gz + gva_A + gva_B_E + 
                 gva_F + gva_G_I + gva_J + gva_K + gva_L + 
                 gva_M_N + gva_O_U, 
               data = data_synth_c, 
               index = c("geo","time"), 
               force = "two-way", 
               CV = TRUE, 
               r = c(0, 4), # an integer specifying the number of factors. If CV = TRUE, the cross validation procedure will select the optimal number of factors from r to 5.
               se = TRUE, 
               # EM = TRUE, # Gobillon and Magnac (takes a lot of time)
               inference = "parametric", nboots = 100,  #500
               parallel = TRUE,
               min.T0 = 6) # Has to be larger than r.max+1

# Idea: include countries/NUTS 2 regions and others as FE to control for heterogeneity?

# NOTE: I need to correct from assigning treatment by a point to assygn treatment by the area. If not, some NUTS3 in Paris and London will be counted as controls! 
# They should eather be treated or cease to be controls [ ]
# !!!
```




```{r}
out2 %>% print()
out2$est.att
out2$est.avg
out2$est.beta
out2$Y.ct %>% as.data.frame() # pred counterfactuals for the treated units.
out2$Y.co %>% as.data.frame()
out2$eff %>% as.data.frame()  # Y - predicted Y(0);
out2$eff.cnt %>% as.data.frame() # Y - predicted Y(0); rearranged based on the timing of the treatment.

# Inspect results, how are the estimated tratement effects for all treated?

out2$eff.cnt %>% as.data.frame() %>% # Y - predicted Y(0);
  rownames_to_column(var = "year") %>% 
  mutate(year = as.numeric(year)) %>%
  pivot_longer(-year, names_to = "geo", 
               values_to = "y_minus_y0") %>%
  left_join(data) -> all_treat_effects

all_treat_effects %>%
  ggplot(aes(x = year, y = y_minus_y0)) +
  geom_line( aes(colour = nuts_name))
# Note: I need to see if this continues to happen for random pacebo treatments 
all_treat_effects
```

_Questions:_ 

* What is the CV procedure of gsynth?
* What is the bootstraping procedure of gsynth?

```{r}
# out2$est.co$residuals %>% as.data.frame()
# plot(out2, ylim = c(-0.4, 0.02))
plot(out2, ylim = c(-5000, 2000))

plot(out2, type = "counterfactual", 
     raw = "all", main="") # Why the final dip?

plot(out2, type = "counterfactual", 
     raw = "none", main="") # Why the final dip?

plot(out2, type = "counterfactual", id = "UKF14") # Nottingham
plot(out2, type = "counterfactual", id = "FR101") # Paris
plot(out2, type = "counterfactual", id = "HU110") # Budapest
plot(out2, type = "counterfactual", id = "DE111") # Stuttgart
plot(out2, type = "counterfactual", id = "DE212") #	München
plot(out2, type = "counterfactual", id = "UKI32") #	Westminster (LDN)
# LONDON BOROUGHS! UKI31 - UKI45
# UKI31	Camden and City of London	
# UKI32	Westminster
# UKI33	Kensington & Chelsea and Hammersmith & Fulham		
# UKI34	Wandsworth		
# UKI41	Hackney and Newham		
# UKI42	Tower Hamlets
# UKI43	Haringey and Islington		
# UKI44	Lewisham and Southwark		
# UKI45	Lambeth
# UKI51	Bexley and Greenwich		
# UKI52	Barking & Dagenham and Havering		
# UKI53	Redbridge and Waltham Forest		
# UKI54	Enfield

data_synth_c %>%
  filter(substr(geo, 1, 2) == "UK") %>%
  arrange(geo) %>%
  filter(geo == "UKI32")

# London (LEZ) initial date (2008) is WRONG, it is the ULEZ one (2019)
# The CCS was introduced in 2003, expansion on 2007
```


## Extras:

### Try to extract kmls (geographies of all LEZ):
_NOTE_: The files are encrypted, I need to deencrip them before. C#.
```{r}
# library(rgdal)
# belg_ghent = readOGR(dsn = "~/A - Estudios/LSE - Applied Social Data Science/Project/PM2.5/Data Europe/BelgienGent.kmls")
# ??readOGR
```

### Good info on spatial analysis:
https://mgimond.github.io/Spatial/uncertainty-in-census-data.html

### Fast and reliable computation of generalized synthetic controls (MSCMT package)
(look at Mendelay paper and to https://cran.r-project.org/web/packages/MSCMT/index.html)

### New methodologies (2019) on multiple timing and periods DiD:
https://andrewcbaker.netlify.com/2019/09/25/difference-in-differences-methodology/

### Abadie and L'Hour code for SCM with penalization for interpolation biases:

https://github.com/jlhourENSAE/regsynth

### RNN - based methods: Predict the synthetic control with NN:
https://ideas.repec.org/p/arx/papers/1712.03553.html

### "CausalInference" the Google made package to estimate Bayesian Structural Time Series Models:
https://google.github.io/CausalImpact/

### Critiques to synth methods with CV if done improperly:
- Look at Mendeley biblography on 04/2020

### Non-parametric Synth (Italian researcher - on STATA)
https://ideas.repec.org/c/boc/bocode/s458398.html
https://www.sciencedirect.com/science/article/pii/S0165176519301788?entityID=https%3A%2F%2Flse.ac.uk%2Fidp&pes=vor 

## Similar analysis with code and other methodologies: (to read and review)
https://andrewcbaker.netlify.com/2020/01/01/what-can-we-say-about-medical-marijuana-and-opioid-overdose-mortality/

## How much pollution comes from cars? (and other info from the EC):
https://ec.europa.eu/environment/air/cleaner_air/

n the notebook, the results appear beneath the code. 

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
