---
title: "Implementation ECI"
author: 'Alessandra Pasquini'
date: ""
output: 
  html_notebook:
  code_folding: show
# keep_md: true
df_print: paged
---
  
The following code returns the total (`tot1`), direct (`dir1`) and indirect (`ind1`) effects implementing MASC method. The lines of the code which does not require user's interaction are labeled as "(automatic)" in the commented lines immediately above.

```{r}
library(Synth)
library(limSolve)
```

## Calculation of total, direct and Indirect effects.

#### Load the database: 

* the name has to be "data"
* it has to have a column of id, 
* numeric id, 
* time
* mediator and
* outcome

```{r}
load("C:/Users/Alessandra/Documents/Dottorato/Visiting/data2.RData")
```

Especify the variables, periods and the delay of the mediator:

```{r}
#Name of the treated unit in the column with ID "col_id"
name_treat<-"FRA"

#Column with ID
col_id<-1
#Column with numeric ID
col_id_num<-7
#Column with time 
col_time<-2

#Mediator column
M<-6
#Outcome column
Y<-4

#Starting pre-treatment period
T_in<-1986
#Ending pre-treatment period
T_fi<-1997
#Ending post-treatment period
T_fi2<-2007
#Number of time periods between a value of the mediator and its impact on the outcome
delay<-1
```

Name of the control units in the column with ID col_id (if the control units are all units in the database except the treated then do not run the two following lines)

```{r}
controls_name<-c("AUS", "SWE", "CAN", "CHE", "GBR","JPN","ISR", "NOR","MYS", "NZL", "USA")
data<-data[which(is.element(data[,col_id], controls_name) | data[,col_id]==name_treat),]

#Create a column with treatment status (automatic)
data<-cbind(data, rep(0, nrow(data)))
data[data[,col_id]==name_treat, ncol(data)]<-1

#Identifies donor pool in the numeric id column (automatic)
controls<-data[!(data[,col_id]==name_treat) & data[,col_time]==T_in, col_id_num]

#Create all the required constraints (automatic) the constraints on all pre-treatment outcome until one year before intervention and pre-treatment mediator until two years before intervention)

## Note Antonio: This depends on the delay.

pretreat4<-list(list(Y, T_in, "mean"))
for (t in c((T_in+1):T_fi)){
   pretreat4[[length(pretreat4)+1]]<-list(Y, t, "mean")
}
for (t in (T_in-delay):(T_fi-delay)){
   pretreat4[[length(pretreat4)+1]]<-list(M, t, "mean")
 }
#If other constraints are needed complete and run the following line 
#(copying and pasting it as much as needed)
#pretreat4[[length(pretreat4)+1]]<-list(column number of the variable, years of interest, "function that has to be applied to the values of that variable in those years")
#Example 1: pretreat4[[length(pretreat4)+1]]<-list(15, 1986:1990, "mean")
#Example 2:
# for (c in 24:37){
#   pretreat4[[length(pretreat4)+1]]<-list(c, 1991:1997, "mean")
# }


#Add fake pre-treatment outcomes to optimize on pre-treatment mediator values (automatic) during 
#the choice of matrix V
#If it is decided to select the weights V to use manually skip these lines of code
data<-data[which(data[,col_time]>=(T_in-delay) & data[,col_time]<=T_fi2),]
data2<-data[which(data[,col_time]>=(T_in-delay) & data[,col_time]<=(T_fi-delay)),]
data2[,Y]<-data2[,M]
data2<-data2[order(data2[,col_id_num],data2[,col_time]),]
data2[,col_time]<-rep((T_in-length(T_in:T_fi)-delay):(T_in-1-delay), length(controls)+1)
data<-rbind(data2, data)
data<-data[order(data[,col_id_num],decreasing=F),]
remove(data2)

#Fake starting time (automatic)
#This starting time is required if the pre-treatment mediator values are added as fake outcomes (see above), otherwise run the commented line below
T_inf<-T_in-length(T_in:T_fi)-delay
#T_inf<-T_in
```

### Total Effect

```{r}
#Looking for the synthetic unit for the estimation of total effect (automatic):
prepar<-dataprep(data, special.predictors=pretreat4, dependent=Y, unit.variable=col_id_num, controls.identifier = controls, time.variable =col_time, treatment.identifier =data[data[,col_id]==name_treat & data[,col_time]==T_in,col_id_num], time.predictors.prior=c(T_inf:(T_in-delay-1), T_in:T_fi), time.optimize.ssr = c(T_inf:(T_in-delay-1), T_in:T_fi), time.plot=T_inf:T_fi2)
sintetico4<-synth(data.prep.obj = prepar)
#If the weights V are chosen manually run the commented line below rather than those above
#sintetico4<-synth(data.prep.obj = prepar, custom.v=required weigths)

#Select the values for the graph of the outcome (and the total effect value) (automatic)
M1<-data[which(data[,ncol(data)]==1 & data[,col_time]>=T_in & data[,col_time]<=T_fi2), Y]
M_synth<-c()
for (u in controls){
  M_synth<-cbind(M_synth, matrix(data[which(data[,col_id_num]==u & data[,col_time]>=T_in & data[,col_time]<=T_fi2), Y], ncol=1))
}
#Plot the results (automatic)
plot(T_in:T_fi2, M1, type="l", ylim=c(min(c(M1, M_synth%*%sintetico4$solution.w))-sd(M1), max(c(M1, M_synth%*%sintetico4$solution.w))+sd(M1)), xlab="Time", ylab="Outcome", main=colnames(data)[Y], sub="Observed Y(1,1) and Synthetic Y(0,0)")
lines(T_in:T_fi2, M_synth%*%sintetico4$solution.w, add=TRUE, col="red")
abline(v=(T_fi+1), lty=3)
#Store the results on total effect and pre and post treatment RMSPE (automatic)
potenz1<-M1
potenz2<-M_synth%*%sintetico4$solution.w
tot1<-potenz1-potenz2
PRE_RMSPE_tot1<-mean(tot1[1:(length(T_in:T_fi))]^2)
POST_RMSPE_tot1<-tot1[(length(T_in:T_fi)+1):length(T_in:T_fi2)]

#Select the values for the graph of the mediator when the total effect is calculated (automatic)
M1<-data[which(data[,ncol(data)]==1 & data[,col_time]>=(T_in-delay) & data[,col_time]<=(T_fi2-delay)), M]
M_synth<-c()
for (u in controls){
  M_synth<-cbind(M_synth, matrix(data[which(data[,col_id_num]==u & data[,col_time]>=(T_in-delay) & data[,col_time]<=(T_fi2-delay)), M], ncol=1))
}
#Plot the results (automatic)
plot(T_in:T_fi2, M1, type="l", ylim=c(min(c(M1, M_synth%*%sintetico4$solution.w))-sd(M1), max(c(M1, M_synth%*%sintetico4$solution.w))+sd(M1)),xlab="Time", ylab="Mediator", main=colnames(data)[M], sub="Observed M(1) and Synthetic M(0)")
lines(T_in:T_fi2, M_synth%*%sintetico4$solution.w, add=TRUE, col="red")
abline(v=(T_fi+1), lty=3)
#Store the results on the effect on the mediator (automatic)
M_tot1<-(M1-M_synth%*%sintetico4$solution.w)
```

### Direct Effect

```{r}
#Use the same pre-treatment constraints (automatic)
pretreat6<-pretreat4
#Creates vectors to store the results (automatic)
potenz1<-as.matrix(rep(NA, length(T_in:T_fi2)), nrow=length(T_in:T_fi), ncol=1)
rownames(potenz1)<-T_in:T_fi2
potenz2<-as.matrix(rep(NA, length(T_in:T_fi2)), nrow=length(T_in:T_fi), ncol=1)
rownames(potenz2)<-T_in:T_fi2
#Apply synth algorithm each post-treatment time period adding each time period an additional 
#constraint on the mediator required for the time period of interest (i.e. given by the time 
#period of interest minus the required delay) (automatic)
j<-1
for (i in (T_fi+1):T_fi2){
  #The weigths to select with V can be chosen adding the post-treatment mediator value as a 
  #fake outcome in the cross validation process if the following commented lines are run. If
  #this choice is made the commented synth function below has to be run instead than the 
  #non-commented ones 
  # data2<-data[which(data[,col_time]==(i-delay)),]
  # data2[,Y]<-data2[,M]
  # data2<-data2[order(data2[,col_id_num],data2[,col_time]),]
  # data2[,col_time]<-rep((T_in-length(T_in:T_fi)-delay-j), length(controls)+1)
  # databis<-rbind(data2, databis)
  # data<-data[order(data[,col_id_num],decreasing=F),]
  # remove(data2)
  # T_inf<-T_in-j
  
  #Add the post-treatment constraint on the mediator for the time period of interest (automatic)
  pretreat6[[length(pretreat6)+1]]<-list(M, i-delay, "mean")
  
  #Looking for the synthetic unit for the estimation of direct effect (automatic):
  prepar6<-dataprep(data, special.predictors=pretreat6, dependent=Y, unit.variable=col_id_num, controls.identifier = controls, time.variable =col_time, treatment.identifier =data[data[,col_id]==name_treat & data[,col_time]==T_in,col_id_num], time.predictors.prior=c(T_inf:(T_in-delay-1), T_in:T_fi), time.optimize.ssr =c(T_inf:(T_in-delay-1), T_in:T_fi), time.plot=T_in:T_fi2)
  sintetico6<-synth(data.prep.obj = prepar6, custom.v =c((1/2)*as.numeric(sintetico4$solution.v),rep((1/(2*j)), j)))
  
  #Store the results in the vectors previously created (automatic)
  potenz1temp<-prepar6$Y1plot
  potenz2temp<-prepar6$Y0plot%*%sintetico6$solution.w
  potenz1[rownames(potenz1)==i]<-potenz1temp[rownames(potenz1temp)==i]
  potenz2[rownames(potenz2)==i]<-potenz2temp[rownames(potenz2temp)==i]
  j<-j+1
}

#Store pre-treatment period values for the synthetic unit selected when the last post-treatment period was the period of interest (automatic)
potenz1[rownames(potenz1)>=T_in & rownames(potenz1)<=T_fi]<-potenz1temp[rownames(potenz1temp)>=T_in & rownames(potenz1temp)<=T_fi]
potenz2[rownames(potenz2)>=T_in & rownames(potenz2)<=T_fi]<-potenz2temp[rownames(potenz2temp)>=T_in & rownames(potenz2temp)<=T_fi]

#Store the results on direct effect and corresponding pre and post treatment RMSPE (automatic)
dir1<-potenz1-potenz2
PRE_RMSPE_dir1<-mean(dir1[1:(length(T_in:T_fi))]^2)
POST_RMSPE_dir1<-dir1[(length(T_in:T_fi)+1):length(T_in:T_fi2)]

#Plot the results (automatic)
plot(T_in:T_fi2, potenz1, type="l", ylim=c(min(c(potenz1, potenz2))-(sd(potenz1)), max(c(potenz1, potenz2))+sd(potenz1)), xlab="Time", ylab="Outcome", main=colnames(data)[Y], sub="Observed Y(1,1) and Synthetic Y(0,1)")
lines(T_in:T_fi2, potenz2, add=TRUE, col="red")
abline(v=(T_fi+1), lty=3)

#Select the values for the graph of the mediator when the direct effect is calculated (automatic)
M1<-data[which(data[,ncol(data)]==1 & data[,col_time]>=(T_in-delay) & data[,col_time]<=(T_fi2-delay)), M] 
M_synth<-c()
for (u in controls){
  M_synth<-cbind(M_synth, matrix(data[which(data[,col_id_num]==u & data[,col_time]>=(T_in-delay) & data[,col_time]<=(T_fi2-delay)), M], ncol=1))
}
#Plot the results (automatic)
plot(T_in:T_fi2, M1, type="l", ylim=c(min(c(M1, M_synth%*%sintetico6$solution.w))-sd(M1), max(c(M1, M_synth%*%sintetico6$solution.w))+sd(M1)), xlab="Time", ylab="Mediator", main=colnames(data)[M], sub="Observed M(1) and Synthetic M(1)")
lines(T_in:T_fi2, M_synth%*%sintetico6$solution.w, add=TRUE, col="red")
abline(v=(T_fi+1), lty=3)

#Store the results on indirect effect and corresponding pre and post treatment RMSPE (automatic)
ind1<-tot1-dir1
PRE_RMSPE_ind1<-mean(ind1[1:(length(T_in:T_fi))]^2)
POST_RMSPE_ind1<-ind1[(length(T_in:T_fi)+1):length(T_in:T_fi2)]

#Plot the results on total, direct and indirect effects in psot-treatment periods (automatic)
plot((T_fi+1):T_fi2, tot1[(length(T_in:T_fi)+1):length(T_in:T_fi2)], ylim=c(min(tot1, dir1, ind1)-max(sd(tot1), sd(dir1), sd(ind1)), max(tot1, dir1, ind1)+max(sd(tot1), sd(dir1), sd(ind1))), type="l", xlab="Time", ylab="Effects", col="red", lwd=3)
lines((T_fi+1):T_fi2, dir1[(length(T_in:T_fi)+1):length(T_in:T_fi2)], col="blue", lwd=3)
lines((T_fi+1):T_fi2, ind1[(length(T_in:T_fi)+1):length(T_in:T_fi2)], col="green", lwd=3)
legend(T_fi2-2, max(tot1, dir1, ind1)+max(sd(tot1), sd(dir1), sd(ind1)), c("Total Effect", "Direct Effect", "Indirect Effect"),fill=c("red", "blue", "green"), bty="n")
abline(h=0)
```
